---
title: "Homework2Regression"
author: "Sabbella Prasanna"
date: "3/21/2021"
output:
  pdf_document: default
  html_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{R message=FALSE, warning=FALSE}

library(tidyverse)
library(caret)
library(dplyr)
library(e1071)

```
## 1. I will be using the bloodbrain data set.

## 2. The outcome variable in the data set is logBBB which is the log of the ratio of the concentration of a compound in the brain and the concentration in blood. The data frame bbbDescr contains 134 different molecular descriptors (predictors) of 208 such compounds. 

- logBBB (outcome)\
Data type = continuous numeric
units = no units
Minimum = 2.15000\
1st Quartile = -0.42250\
Median = 0.02000\
Mean = -0.01889\
3rd Quartile = 0.53000\   
Maximum = 1.64000\
Skewness = -0.4639672
           
```{R message=FALSE, warning=FALSE}
data(BloodBrain)
logBBB_df=data.frame(logBBB)
ggplot(logBBB_df,aes(x=logBBB))+geom_histogram()
#skewness(logBBB_df$logBBB)
```

# 3. Splitted the rows for training and testing 60% - 40%

# 4. Model type and RMSE
```{r message=FALSE, warning=FALSE}
set.seed(10)

blood_brain = cbind(bbbDescr, logBBB)

blood_brain_var <- nearZeroVar(blood_brain)
blood_brain_collinear <- findLinearCombos(cov(blood_brain))$remove
blood_brain_main <- blood_brain[, -c(blood_brain_var, blood_brain_collinear)]


training <- blood_brain_main$logBBB %>%
  createDataPartition(p = 0.6, list = FALSE)
blood_brain_main_train  <- blood_brain_main[training, ]
blood_brain_main_test <- blood_brain_main[-training, ]


folds <- createFolds(blood_brain_main$logBBB, k = 10, returnTrain = TRUE)
ctrl <- trainControl(method = "cv", index = folds)

```




# linear regression with RMSE = 1.819
```{r message=FALSE, warning=FALSE}

#lmTuneFiltered <- train(x = blood_brain_processed_train_data,
#                        y = blood_brain_processed_train_data$logBBB,
#                        method = "lm",
#                        trControl = ctrl)

linear_regression_model = lm(logBBB ~., data = blood_brain_main_train)
predictions = linear_regression_model %>% predict(blood_brain_main_test)
RMSE = RMSE(predictions, blood_brain_main_test$logBBB)

RMSE

```
# Regression tree with RMSE = 0.77
```{r message=FALSE, warning=FALSE}

set.seed(12)
regressionTree <- train(
  logBBB ~., data = blood_brain_main_train, method = "rpart",
  trControl = trainControl("cv", number = 10),
  tuneLength = 10)

predictions <- regressionTree %>% predict(blood_brain_main_test)
#head(predictions)
# Compute the prediction error RMSE
RMSE(predictions, blood_brain_main_test$logBBB)


```




# Neural nets with RMSE = 0.62
```{r message=FALSE, warning=FALSE}
nnetGrid <- expand.grid(
decay = c(0.0, 5.0, 20.0, 80.0, 100.0),size = c(3),bag = FALSE)
set.seed(100)
avNNet_model <- train(logBBB ~., data = blood_brain_main_train,
                        method = "avNNet",
                        repeats = 3,
                        tuneGrid = nnetGrid,
                        trControl = trainControl("cv", number = 10),
                        preProc = c("center", "scale"),
                        linout = TRUE,
                        trace = FALSE)

predictions <- avNNet_model %>% predict(blood_brain_main_test)

RMSE(predictions, blood_brain_main_test$logBBB)

```
# knn with RMSE = 0.705
```{r  message=FALSE, warning=FALSE}
set.seed(123)
modelknn <- train(
  logBBB~., data = blood_brain_main_train, method = "knn",
  trControl = trainControl("cv", number = 10),
  preProcess = c("center","scale","BoxCox"),
  tuneLength = 10)

# Make predictions on the test data
predictions <- modelknn %>% predict(blood_brain_main_test)
#head(predictions)
# Compute the prediction error RMSE
RMSE(predictions, blood_brain_main_test$logBBB)


```

# 5. Model parameter comparison with RMSE
```{r message=FALSE, warning=FALSE}
plot(modelknn)
plot(avNNet_model)
plot(regressionTree)
```

# 6. Best RMSE model
- The least RMSE is achieved with avNNet_model with a value of 0.62
